Human capital mediates natural selection in contemporary humans

### 2022-03-19 why-natural-selection.Rmd
Use alternative plot with shapes

@@

standard_ggplot(res_fe_fertility, fill_col = Regression, n_regs = n_regs,
                  fill_direction = -1)

>>>>

  if (is.null(conf_int)) conf_int <- "conf.low" %in% names(dfr)
  confint_geom_segment <- if (conf_int) confint_geom_segment() else NULL

  dfr %>% mutate(
    !! score_col := pretty_names(!! score_col),
    !! score_col := fct_reorder(!! score_col, estimate, order_abs(order_idx))
  ) %>% 
    rename(p = p.value) %>% 
    ggplot(aes(estimate, {{score_col}}, yend = {{score_col}}, 
               shape = {{fill_col}}, ...)) +
    my_vline + 
    confint_geom_segment +
    geom_point(size = 1.8, aes(color = {{fill_col}})) +
    geom_point(size = 0.7, color = "white", aes(alpha = p < 0.05/33)) +
    my_fill_scale(aesthetics = "color", n = n_cats, direction = fill_direction) +
    scale_shape_manual(values = 1:n_cats + 14) +
    my_labs() +
    my_theme() +
    scale_linetype_manual(name = "", values = c("95% c.i." = 1)) +
    scale_alpha_discrete(range = c(1, 0),
                         guide = guide_legend(
                           override.aes = list(
                             shape = c(1, 16),
                             color = "black",
                             alpha = 1,
                             size = 1.8
                           )
                         ))
}

old_ggplot <- function (
        dfr, 
        fill_col, 
        n_regs, 
        ...,
        score_col = quo(term), 
        order_idx = 1, 
        fill_direction = 1,
        n_cats    = NULL,
        conf_int  = NULL
      ) {
  if (! missing(score_col)) score_col <- enquo(score_col)

@@

standard_ggplot(res_fe_fertility, fill_col = Regression, n_regs = n_regs,
                  fill_direction = -1) +
  guides(alpha = guide_legend(
                   override.aes = list(
                             shape = 1,
                             color = "black",
                             alpha = 1,
                             size = 1.8
                   )
                 )
  )
